---
title: "TidyTemplate"
date: 2021-09-21
editor_options: 
  chunk_output_type: console
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(lubridate)
library(ggplot2)
library(tidyr)
theme_set(theme_light())

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tidytuesdayR::tt_load('2021-06-29')


```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

Splitting the date & time from "date_time_of_call" into separate columns
```{r}
hour <- format(as.POSIXct(strptime(tt$animal_rescues$date_time_of_call,"%d/%m/%Y %H:%M",tz="")) ,format = "%H:%M")
dates <- format(as.POSIXct(strptime(tt$animal_rescues$date_time_of_call,"%d/%m/%Y %H:%M",tz="")) ,format = "%d/%d/%Y")

tt$animal_rescues$date <- dates
tt$animal_rescues$time <- hour

```


```{r}
rescues <- tt$animal_rescues %>% 
  drop_na() %>%  
  select(-date_time_of_call,
         -hourly_notional_cost,
         -pump_count,
         -pump_hours_total,
         -uprn,-usrn,
         -easting_m,
         -northing_m,
         -easting_rounded,
         -northing_rounded,
         -final_description)
```


```{r}
rescues$incident_notional_cost <- as.numeric(rescues$incident_notional_cost)
```

```{r}
animals_agg <-
  rescues %>% 
  mutate(
    animal_group_aggregated = case_when(
      str_detect(animal_group_parent, "Domestic|Livestock|Farm|Horse|Cow|Sheep|Goat|Lamb|Bull") ~ "Other Domestic Animals",
      animal_group_parent %in% c("Cat", "cat") ~ "Cats",
      animal_group_parent %in% c("Bird", "Budgie") ~ "Birds",
      animal_group_parent == "Dog" ~ "Dogs",
      animal_group_parent == "Fox" ~ "Foxes",
      TRUE ~ "Other Wild Animals"
    )
  )


```

```{r}
animals_agg %>% 
  #filter(special_service_type_category == "Other animal assistance") %>% 
  count(animal_group_aggregated, sort = TRUE)
```


# Number of rescues each year by type of animal
```{r}
animals_agg %>% 
  ggplot(aes(cal_year, fill = animal_group_aggregated)) +
  geom_bar() +
  labs(title = "Number of rescues per year",
       subtitle = "Split into animal categories",
       fill = "Animal Type",
       x = "Year",
       y = "Number of Rescues")
```

```{r}
animals_agg %>% 
  count(animal_group_aggregated, longitude, latitude, sort = TRUE) %>% 
  ggplot(aes(longitude, latitude, size = n, colour = animal_group_aggregated)) +
  geom_point() +
  scale_size_continuous()
```

